---
title: "Getting started"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{getting-started}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse  = FALSE,
  echo      = TRUE,
  message   = TRUE, 
  warning   = FALSE,
  error     = TRUE,
  comment   = "#>",
  dpi       = 600, 
  out.width = "100%"
  )
```

```{r setup}
library(procedural)
library(icd10us)
library(tidyverse)
library(gt)
library(janitor)
```


The __ICD-10-PCS__, or the __International Classification of Diseases, 10th Revision, Procedure Coding System__, is a procedure classification system developed by 3M Health Information Systems and adopted under HIPAA for classifying procedures performed in hospital inpatient health care settings.

# Coding Conventions

ICD-10-PCS codes are composed of __seven__ alphanumeric characters. Each character contains up to __34__ possible values. The seven characters that make up a complete code have specific meanings that vary for each of the __17__ sections of the manual.

Each value represents a specific option for the general character definition. 10 digits (`0-9`) and 24 letters (`A-H`, `J-N`, and `P-Z`) may be used in each character. The letters `O` and `I` are not used so as to avoid confusion with the digits `0` and `1`.

```{r echo=FALSE, eval=FALSE}
length(c(0:9, LETTERS[c(1:8, 10:14, 16:26)]))
c(0:9, LETTERS[c(1:8, 10:14, 16:26)])
stringr::str_flatten_comma(c(0:9, LETTERS[c(1:8, 10:14, 16:26)]), last = ", and ")
```

## Axes
Each character is an axis of classification that specifies information about the procedure performed. 

Within a defined code range, a character specifies the same type of information in that axis of classification.

For example, The __fifth__ axis of classification specifies the _Approach_ in sections 0 through 4 and 7 through 9 of the system.


```{r}
tibble(
  axis = 1:7,
  name = c('Section',
              'Body System',
              'Root Operation',
              'Body Part',
              'Approach',
              'Device',
              'Qualifier')) |> 
  gt() |> 
  #cols_align(align = 'center') |> 
  opt_table_font(font = google_font(name = "Fira Code")) |> 
  opt_table_lines(extent = "all") |> 
  opt_all_caps()
```


```{r echo=FALSE, eval=FALSE}
tibble(
  AXIS = "NAME",
  `1` = "Section",
  `2` = "Body System",
  `3` = "Root Operation",
  `4` = "Body Part",
  `5` = "Approach",
  `6` = "Device",
  `7` = "Qualifier") |> 
  gt() |> 
  cols_align(align = 'center') |> 
  opt_table_lines(extent = "all") |> 
  opt_all_caps()
```

# Section

```{r}
section() |> 
  gt() |> 
  opt_table_lines(extent = "all") 
```


# Axis

```{r}
axis("0")
```



