---
title: "Getting started"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{getting-started}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse  = FALSE,
  echo      = TRUE,
  message   = TRUE, 
  warning   = FALSE,
  error     = TRUE,
  comment   = "#>",
  dpi       = 600, 
  out.width = "100%"
  )
```

```{r setup, message=FALSE, warning=FALSE}
library(procedural)
library(dplyr)
library(gt)
```


The __ICD-10-PCS__, or the __International Classification of Diseases, 10th Revision, Procedure Coding System__, is a procedure classification system developed by 3M Health Information Systems and adopted under HIPAA for classifying procedures performed in hospital inpatient health care settings.

# Coding Conventions

ICD-10-PCS codes are composed of __seven__ alphanumeric characters. Each character contains up to __34__ possible values. The seven characters that make up a complete code have specific meanings that vary for each of the __17__ sections of the manual.

Each value represents a specific option for the general character definition. 10 digits (`0-9`) and 24 letters (`A-H`, `J-N`, and `P-Z`) may be used in each character. The letters `O` and `I` are not used so as to avoid confusion with the digits `0` and `1`.

```{r echo=FALSE, eval=FALSE}
length(c(0:9, LETTERS[c(1:8, 10:14, 16:26)]))
c(0:9, LETTERS[c(1:8, 10:14, 16:26)])
stringr::str_flatten_comma(c(0:9, LETTERS[c(1:8, 10:14, 16:26)]), last = ", and ")
```

## Axes

Each character is an axis of classification that specifies information about the procedure performed. 

Within a defined code range, a character specifies the same type of information in that axis of classification.

For example, The __fifth__ axis of classification specifies the _Approach_ in sections 0 through 4 and 7 through 9 of the system.


```{r}
tibble(
  axis = 1:7,
  name = c('Section',
              'Body System',
              'Root Operation',
              'Body Part',
              'Approach',
              'Device',
              'Qualifier')) |> 
  gt() |> 
  opt_table_font(font = google_font(name = "Rubik")) |> 
  opt_table_lines(extent = "all") |> 
  opt_all_caps()
```


```{r echo=FALSE, eval=FALSE}
tibble(
  AXIS = "NAME",
  `1` = "Section",
  `2` = "Body System",
  `3` = "Root Operation",
  `4` = "Body Part",
  `5` = "Approach",
  `6` = "Device",
  `7` = "Qualifier") |> 
  gt() |> 
  cols_align(align = 'center') |> 
  opt_table_font(font = google_font(name = "Rubik")) |> 
  opt_table_lines(extent = "all") |> 
  opt_all_caps()
```


# Sections

```{r}
sections()
```


```{r}
sections()[c('code', 'label')] |> 
  gt() |> 
  opt_table_font(font = google_font(name = "Rubik")) |> 
  cols_align(align = "center", columns = code) |>
  tab_style(style = list(cell_fill(color = "lightgray", alpha = 0.5), 
                         cell_text(weight = "bold")), 
            locations = cells_body(columns = code)) |> 
  opt_all_caps() |> 
  opt_align_table_header(align = "left") |>
  tab_header(title = md("**ICD-10-PCS** Sections"))
```

# Systems

```{r}
systems()
```

# Tables

```{r}
# BR Imaging, Axial Skeleton, Except Skull and Facial Bones
# C9 Nuclear Medicine Ear, Nose, Mouth and Throat
# D9 Radiation Therapy Ear, Nose, Mouth and Throat
# G Mental Health
# H Substance Abuse Treatment
tables("gz") |> tidyr::unnest(codes)
```


# Definitions

```{r}
definitions() |> 
  summarise(n = n(), 
            .by = c(code, section, axis, axis_name))
```

```{r}
definitions() |>
  filter(
    code == "0" 
    ,axis == "3" 
    ,label == "Bypass"
    )
```



## Medical and Surgical

```{r echo=FALSE, eval=FALSE}
bypass <- definitions() |>
  dplyr::filter(code == "0", axis == "3", label == "Bypass") |>
  dplyr::select(label, definition, explanation, includes)

code <- pcs("0016070")

x <- dplyr::left_join(code, bypass, by = dplyr::join_by(label))
```


```{r}
pcs("0016070") |> 
  gt(rowname_col = "axis") |> 
  opt_table_font(font = google_font(name = "Rubik")) |> 
  cols_align(align = "center", columns = c(axis, code)) |>
  tab_style(style = list(cell_fill(color = "lightgray", 
                                   alpha = 0.5), 
                         cell_text(weight = "bold")), 
            locations = cells_body(columns = code)) |> 
  opt_all_caps() |> 
  opt_align_table_header(align = "left") |>
  tab_header(title = html("<b>ICD-10-PCS</b> 2024<hr>"),
             subtitle = html("<small>SECTION:</small> <b>0</b> Medical and Surgical<br>
                              <small>SYSTEM:</small> <b>0</b> Central Nervous System and Cranial Nerves<br>
                              <small>OPERATION:</small> <b>1</b> Bypass<br><br>")) |> 
  sub_missing(missing_text = "")
```

