---
title: "Getting started"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{getting-started}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse  = TRUE,
  echo      = TRUE,
  message   = TRUE, 
  warning   = FALSE,
  error     = TRUE,
  comment   = "#>",
  dpi       = 600, 
  out.width = "100%"
  )
```

```{r setup, message=FALSE, warning=FALSE}
library(procedural)
library(fuimus)
library(dplyr)
library(gt)
library(htmltools)
```


__ICD-10-PCS__, or the __International Classification of Diseases, 10th Revision, Procedure Coding System__, is a procedure classification system developed by [3M](https://www.3m.com/3M/en_US/health-information-systems-us/) and adopted under [HIPAA](https://en.wikipedia.org/wiki/Health_Insurance_Portability_and_Accountability_Act) for classifying procedures performed in hospital inpatient health care settings.

<br>

# Overview

WHO has maintained the International Classification of Diseases (ICD) for recording causes of death since 1893. It has updated the ICD periodically to reflect new discoveries in epidemiology and changes in medical understanding of disease. CMS contracted with 3M Health Information Systems in 1993 to design and develop a procedural classification system that would replace Volume 3 of ICD-9-CM. ICD-10-PCS was initially released in 1998 and is updated annually.

# Structure

An ICD-10-PCS code is best understood as the result of a process rather than as an assigned number.

All valid codes in ICD-10-PCS are seven characters long. Each character represents an aspect of the procedure, as shown in the following diagram of characters from the main section of ICD-10-PCS, Medical and Surgical:

Individual letters and numbers, called **values**, are selected in sequence to occupy the seven spaces of the code, called **characters**.




```{r echo=FALSE}
tibble(
  Axis = 1:7,
  Name = c(
    'Section',
    'Body System',
    'Root Operation',
    'Body Part',
    'Approach',
    'Device',
    'Qualifier'
  )
) |> 
  gt() |> 
  tab_style(
    style = list(
      cell_fill(color = "lightgray",
                alpha = 0.5),
      cell_text(weight = "bold")),
    locations = cells_body(columns = Axis)) |>
  cols_align(align = 'center', 
             columns = Axis) |>
  opt_table_font(font = google_font(name = "Rubik")) |>
  opt_all_caps() |>
  opt_table_outline(style = "none") |> 
  tab_options(
    table.width = pct(75),
    heading.title.font.size = px(18),
    heading.subtitle.font.size = px(14),
    heading.align = "left",
    table.font.color = "#0B0B45",
    footnotes.font.size = px(12),
    footnotes.marks = letters
    )
```   



## Values

One of 34 possible values can be assigned to each character in a code: the integers 0–9 and the alphabet (except I and O, because they are easily confused with the numbers 1 and 0). A finished code looks like the example below.

> **02103D4** *Bypass coronary artery, one artery from coronary vein with intraluminal device, percutaneous approach*


```{r}
x <- pcs("02103D4")

x$axes |>
  gt(rowname_col = "axis") |>
  cols_align(align = "center", columns = c(axis, value)) |>
  tab_style(style = list(cell_fill(color = "lightgray",
                                   alpha = 0.5),
                         cell_text(weight = "bold")),
            locations = cells_body(columns = value)) |>
  tab_header(subtitle = html("<b><i>ICD-10-PCS 2024</i></b>"),
             title = html(paste0("<b><u>", 
                                 x$procedure$code, "</u></b> ", 
                                 x$procedure$description))) |>
  tab_footnote(
    footnote = html(paste0("<b>Definition:</b> ", 
    x$definitions$definition[1])),
    locations = cells_body(columns = label, rows = 3)) |>
  tab_footnote(
    footnote = html(paste0("<b>Definition:</b> ", 
    x$definitions$definition[2])),
    locations = cells_body(columns = label, rows = 5)) |>
  opt_table_font(font = google_font(name = "Rubik")) |>
  opt_all_caps() |>
  opt_table_outline(style = "none") |> 
  tab_options(
    table.width = pct(75),
    heading.title.font.size = px(18),
    heading.subtitle.font.size = px(14),
    heading.align = "left",
    table.font.color = "#0B0B45",
    footnotes.font.size = px(12),
    footnotes.marks = letters,
    column_labels.hidden = TRUE)
```



Choosing a specific value for each of the seven characters derives this code. Based on details about the procedure performed, values for each character specifying the **section**, **body system**, **root operation**, **body part**, **approach**, **device**, and **qualifier** are assigned.

Because the definition of each character is a function of its actual physical position in the code, the same value placed in a different position in the code means something totally different. 


## Organization

ICD-10-PCS is composed of 17 sections, represented by the numbers 0-9 and the letters B-D, F-H and X. 

The machinery of PCS is contained in three parts: the **Index**, the **Tables**, and the **List of Codes**. 


Additionally, there are **Appendices** that contain information about the structure of the code set and the definitions of the values used in the code.

There is also a list of guidelines in the ICD-10-PCS code book that instruct you on how to use the PCS code set.

### Medical and Surgical Section

The first section, Medical and Surgical, contains the majority of procedures typically reported in an inpatient setting.

__Coding Example__

The example below describes the excision of a dorsal ganglion located at the wrist level. A PCS code is built by selecting the appropriate characters to describe the _intent_, the _approach_, and other _qualifying information_ on how the procedure is performed.

> Note: The purpose of the ICD-10-PCS code is to explain the purpose of the procedure by using every character to describe the way the procedure was performed.


__Operative Report:__ *Excision of Dorsal Ganglion, Right Wrist*

With the patient under adequate anesthesia, the right upper extremity was prepped and draped in a sterile manner. The arm was exsanguinated and the tourniquet was elevated to 290 mm/Hg. A transverse incision was made over the dorsal ganglion. Using blunt dissection the dorsal ulnar sensory nerve branches and radial sensory nerve branches were dissected and retracted out of the operative field. 

The extensor tendon was then incised, dissected, and retracted out of the operative field. The ganglion was then further dissected to its origin from the dorsal distal scapholunate interosseus ligament and excised. Care was taken to protect ligament integrity. The wound was then infiltrated with 0.25% Marcaine. The tendons were allowed to resume their normal anatomical position. The skin was closed with 3-0 Prolene subcuticular stitch. Sterile dressings were applied. The tourniquet was deflated.

   1. Section **0** Medical and Surgical
   1. Body System **L** Tendons (Extensor tendon)
   1. Root Operation **B** Excision (The tendon was excised and removed)
   1. Body Part **5** Lower Arm, and Wrist, Right (The extensor tendon is located at the wrist level)
   1. Approach **0** Open (An incision was performed and blunt dissection carried out through layers of tissue to expose site)
   1. Device **Z** No Device
   1. Qualifier **Z** No Qualifier


```{r}
x <- pcs("0LB50ZX")

x$axes |>
  gt(rowname_col = "axis") |>
  opt_table_font(font = google_font(name = "Rubik")) |>
  cols_align(align = "center", columns = c(axis, value)) |>
  tab_style(style = list(cell_fill(color = "lightgray",
                                   alpha = 0.5),
                         cell_text(weight = "bold")),
            locations = cells_body(columns = value)) |>
  opt_all_caps() |>
  opt_table_outline(style = "none") |>
  tab_header(subtitle = html("<b><i>ICD-10-PCS 2024</i></b>"),
             title = html(paste0("<b><u>", 
                                 x$procedure$code, "</u></b> ", 
                                 x$procedure$description))) |>
  tab_footnote(
    footnote = html(paste0("<b>Definition:</b> ", 
    x$definitions$definition[1])),
    locations = cells_body(columns = label, rows = 3)) |>
  tab_footnote(
    footnote = html(paste0("<b>Definition:</b> ", 
    x$definitions$definition[2])),
    locations = cells_body(columns = label, rows = 5)) |>
  tab_options(
    table.width = pct(75),
    heading.title.font.size = px(18),
    heading.subtitle.font.size = px(14),
    heading.align = "left",
    table.font.color = "#0B0B45",
    footnotes.font.size = px(12),
    column_labels.hidden = TRUE)
```

## Medical and Surgical Related Sections

Sections 0-9 of ICD-10-PCS comprise the Medical and Surgical Related sections. These sections include obstetrical procedures, administration of substances, measurement and monitoring of body functions, and extracorporeal therapies, as listed in the table below.

```{r echo=FALSE}
procedural:::sections(0:9)[c('value', 'label')] |> 
  gt(rowname_col = "value") |>
  opt_table_font(font = google_font(name = "Rubik")) |>
  opt_all_caps() |>
  tab_header(title = md("**Medical and Surgical-Related Sections**")) |>
  tab_options(
    table.width = pct(75),
    heading.title.font.size = px(18),
    heading.subtitle.font.size = px(14),
    heading.align = "left",
    table.font.color = "#0B0B45",
    footnotes.font.size = px(12),
    column_labels.hidden = TRUE)
```


```{r echo=FALSE, eval=FALSE}
tables() |> 
  group_by(section) |>
  summarise(codes = sum(n_codes),
            prop = codes / 78220) |>
  rename(code = section) |> 
  left_join(sections()[c('code', 'label')], 
            by = join_by(code)) |> 
  select(code, label, codes, prop) |> 
  mutate(id = row_number(), .before = 1) |>
  gt(rowname_col = "id") |> 
  fmt_percent(columns = prop, decimals = 1) |>
  fmt_number(columns = codes, decimals = 0) |>
  opt_table_font(font = google_font(name = "Rubik")) |> 
  cols_align(align = "center", columns = code) |>
  cols_hide(c(codes, prop)) |> 
  tab_style(style = list(cell_fill(color = "lightgray", 
                                   alpha = 0.5), 
                         cell_text(weight = "bold")), 
            locations = cells_body(columns = code)) |> 
  opt_all_caps() |> 
  opt_align_table_header(align = "left") |>
  tab_header(title = md("**ICD-10-PCS 2024** Sections")) |> 
  cols_nanoplot(columns = codes, 
                plot_type = "bar", 
                new_col_label = "# of Codes",
                options = nanoplot_options(
                  data_bar_fill_color = "#0B0B45",
                  data_bar_stroke_color = "#0B0B45",
                  interactive_data_values = FALSE)) |>
  tab_style(style = cell_borders(sides = c("left"), 
                                 weight = "5px", 
                                 color = "lightgray"),
            locations = cells_body(columns = nanoplots))
```


In sections 0, 1, and 2, all seven characters define the same aspects of the procedure.

Sections 3-9 are differ only slightly. For example, in sections 5 and 6, the 5th character is defined as Duration instead of Approach, as in this code for _Intra-aortic Balloon Pump (IABP)_:


```{r}
x <- pcs("5A02210")

x$axes |>
  gt(rowname_col = "axis") |>
  opt_table_font(font = google_font(name = "Rubik")) |>
  cols_align(align = "center", columns = c(axis, value)) |>
  tab_style(style = list(cell_fill(color = "lightgray",
                                   alpha = 0.5),
                         cell_text(weight = "bold")),
            locations = cells_body(columns = value)) |>
  opt_all_caps() |>
  opt_table_outline(style = "none") |>
  tab_header(
    title = html(paste0("<b>", x$code, "</b>  ", x$description)),
    subtitle = tagList(tags$div(style = css(`text-align` = "right"), 
                                tags$div(tags$strong("ICD-10-PCS 2024"))))) |>
  tab_options(
    stub.background.color = "#0B0B35",
    stub.border.color = "white",
    stub_row_group.border.color = "#0B0B35",
    table.width = pct(75),
    heading.title.font.size = px(16),
    heading.subtitle.font.size = px(14),
    heading.background.color = "white",
    heading.border.bottom.color = "#0B0B35",
    heading.align = "left",
    table.font.color = "#0B0B35",
    table.font.size = px(14),
    table.border.bottom.color = "#0B0B35",
    footnotes.font.size = px(12),
    column_labels.hidden = TRUE)
```


### Ancillary Sections

Sections B - D and F - H comprise the ancillary sections:


```{r, echo=FALSE}
procedural::sections(c("B", "C", "D", "F", "G", "H", "X"))[c('value', 'label')] |> 
  gt(rowname_col = "value") |>
  opt_table_font(font = google_font(name = "Rubik")) |>
  opt_all_caps() |>
  tab_header(title = md("**Ancillary Sections**")) |>
  tab_options(
    table.width = pct(75),
    heading.title.font.size = px(18),
    heading.subtitle.font.size = px(14),
    heading.align = "left",
    table.font.color = "#0B0B45",
    footnotes.font.size = px(12),
    column_labels.hidden = TRUE)
```

When coding for CT scans, the documentation must support all components for proper selection of the ICD-10-PCS code. The section for the first character will come from the Imaging section. The body system will be based on the area that is examined. The root type will be determined by the type of imaging (CT, MRI, X-ray). The body part is selected by determining the specific body area that was analyzed during the procedure. The contrast character is used to determine if high osmolar, low osmolar, or other type of contrast was used, if applicable. The qualifier character will be used to specify if enhanced or unenhanced images were taken.

> **Example**: CT scan of brain
>> Technique: 2.5 mm thick axial images were obtained through the head with diatrizoate (high osmolar contrast). 
>> 0.625 mm thick axial images as well as coronal and sagittal enhanced images were also submitted for interpretation.

> **Findings**:
>> No intra- or extra-axial blood or fluid collection is present. There is no mass or shift of midline. Brain densities are normal. The 
>> ventricles and sulci are normal in size and configuration. Vascular structures are normal in appearance. The pituitary, orbits, and 
>> paranasal sinuses are unremarkable. The calvarium is intact.


```{r}
x <- pcs("B02000Z")

x$axes |>
  gt(rowname_col = "axis") |>
  opt_table_font(font = google_font(name = "Rubik")) |>
  cols_align(align = "center", columns = c(axis, value)) |>
  tab_style(style = list(cell_fill(color = "lightgray",
                                   alpha = 0.5),
                         cell_text(weight = "bold")),
            locations = cells_body(columns = value)) |>
  opt_all_caps() |>
  tab_header(title = html("<b>ICD-10-PCS 2024</b>"),
             subtitle = html(paste0("<b>", x$code, ": </b>", x$description))) |>
  tab_options(
    table.width = pct(55),
    heading.title.font.size = px(20),
    heading.subtitle.font.size = px(14),
    heading.align = "left",
    table.font.color = "#0B0B45",
    footnotes.font.size = px(12))
```


Section X defines the 7th character as the New Technology Group. This letter changes each year that new technology codes are added to the system. 

For example, Section X codes added for the first year have the 7th character value 1, New Technology Group 1. The next year that contains new Section X codes the 7th character value is 2, for New Technology Group 2, etc.


# Index


The ICD-10-PCS Index can be used to access the Tables. The Index mirrors the structure of the Tables, so it follows a consistent pattern of organization and use of hierarchies.

## Main terms

The Index is organized as an alphabetic lookup. Two types of main terms are listed in the Index:

   + Based on the value of the 3rd character
   + Common procedure terms

For the Medical and Surgical and Related sections, the root operation values are used as main terms in the Index. In other sections, the values representing the general type of procedure performed, such as nuclear medicine or imaging type, are listed as main terms.

For the Medical and Surgical and Related sections, values such as excision, bypass, and transplantation are included as main terms in the index. The applicable body system entries are listed beneath the main term and refer to a specific table. For the ancillary sections, values such as fluoroscopy and positron emission tomography are listed as main terms.

The index entry **Bypass** refers to the Medical and Surgical section tables for all applicable body systems, including anatomical regions and central nervous system:

   + Bypass
      + by Body System
         + Peritoneal Cavity 0W1G
         + Spinal Canal 001U

The Body System listings may be followed by entries for specific body parts:

   + Artery
   + Anterior Chamber
     + Left 08133
     + Right 08123
   + Axillary
     + Left 03160
     + Right 03150
   + Brachial
     + Left 03180
     + Right 03170
   + Common Carotid
     + Left 031J0
     + Right 031H0

In the root operations change, insertion, removal, and revision, the device entries are further defined by the body part the device is inserted into/or on.


## Common Procedure Terms

The second type of term listed in the Index uses procedure names, such as "appendectomy" or "fundoplication". 

These entries are listed as main terms, and refer to a table or tables from which a valid code can be constructed, as shown in the following example:

   + Cholecystectomy
      + see Excision, Gallbladder 0FB4
      + see Resection, Gallbladder 0FT4

When two or more root operations are listed for a procedure, you must study the operative report to determine which root operation was documented as the purpose of the procedure. 

For example, excision means to cut out or off a portion of a body part, while resection means to cut out or off ALL of the body part. If all of the gallbladder is removed, code to resection of gallbladder.


# Tables

Tables are organized in a series, beginning with section 0, medical and surgical, and body system 0, central nervous, and proceeding in numerical order. Sections 0-9 are followed by sections B-D and F-H. The same convention is followed within each table for the second through the 7th characters — numeric values in order first, followed by alphabetical values in order.

The following examples use the Medical and Surgical section to describe the organization and format of the ICD-10-PCS tables.

The Medical and Surgical section (1st character 0) is organized by its 31 body system values. Each body system subdivision in the Medical and Surgical section contains an introductory table that lists the possible values for the remaining characters, given that body system.

The Tables section is what is used to construct complete and valid codes. Based on the first three values of the code provided in the Index, the corresponding table can be located. The tables and characters are arranged by number, then by letter for each character.

The root operation tables consist of four columns and a varying number of rows, as in the following example of the root operation Bypass, in the Central Nervous body system.

Section 
Body System 
Root Operation

The below operative report will describe ventriculoperitoneal (VP) shunt placement. The purpose of a VP shunt is for a valve to be placed into your head, with one catheter being placed in the cerebral ventricle and the other end in the peritoneal cavity. Patients who require a VP shunt tend to be diagnosed with hydrocephalus, which is a condition where there is an accumulation of cerebrospinal fluid (CSF) in the ventricles. The shunt removes the accumulated fluid from the brain into the peritoneal cavity.

Operative Report: VP shunt placement

The first incision was made at the level of the frontal area, and coagulation was used to control bleeding. Then, another incision was made at the level of the abdominal wall, and by using a tunneler, the peritoneal catheter was passed from the abdominal wall to the posterior parietal, where a small incision was also made and then up to the right frontal area. The catheter was primed, and the catheter used was a Bactiseal. Then, the programmable valve was set at 180 mm of water and was connected to the peritoneal catheter. At this point, using a previous bur hole, the Bactiseal ventricular catheter was soft passed into the ventricle and connected to the programmable valve. All of these areas of connection were then verified. Then, the peritoneal catheter was inserted into the peritoneal cavity, which was dissected in layers starting from the rectus muscle and then to the peritoneum. The catheter was introduced into the peritoneal cavity after verification of the dripping of CSF.

00160J6 
Bypass cerebral ventricle to peritoneal cavity with synthetic substitute, open approach

When reviewing the description of the ICD-10-PCS code, you will notice the intent of the procedure is described with the root operation bypass, which is defined as altering the route of passage of the contents of a tubular body part. The highlighted keywords help determine the proper selection of the code, for example, the procedure required an incision in the frontal area and the abdominal wall to be able to insert the catheter. This will justify the character of “open” approach.

The values for characters 1-3 are provided at the top of each table. Four columns contain the applicable values for characters 4-7, given the values in characters 1-3.

A table may be separated into rows to specify the valid choices of values in characters 4-7. A code built using values from more than one row of a table is not a valid code. In the table above, there are only five choices for the 7th character of Body Part, U, Spinal Canal. You can’t cross the line to choose a 7th character from the row above.

## Appendices

There are many tables in ICD-10-PCS besides the tables used to construct the codes. The appendices in the ICD-10-PCS code book contain many helpful tables.

### Appendix A
contains a table that defines all root operations in the ICD-10-PCS code book. It lists not only the definition, but also an explanation and example(s) for each root operation. The root operations are listed by character value, in numeric order, followed by alphabetical order. For example, Root Operations - Alteration is listed with Definition, Explanation, and Examples such as face lift and breast augmentation.

### Appendix B
is a Body Part Key. This is a very helpful tool to help match a specific body part to a descriptor in ICD-10-PCS. It is listed in alphabetic order.

### Appendix C
is a Device Key. Similar to the body part key, it matches a device to a descriptor in ICD-10-PCS. For example, Brachytherapy seeds leads to Radioactive Element.

### Appendix D
is the Device Aggregation Table. This table crosswalks specific device character value definitions for specific root operation in a specific body system to the more general device character value to be used. For example, the specific device Autologous Arterial Tissue, for all applicable operations in the heart and great vessels, lower arteries, lower veins, upper arteries, and upper veins leads to a General Device of 7 Autologous Tissue Substitute.

### Appendix E
contains the Character Meanings tables. This gives an overview of the codes for an entire system in one place.

### Appendix F
contains the Substance Key. This table provides the substance term and then the corresponding ICD-10-PCS Value. For example, Seprafilm® has an ICD-10-PCS Value as an adhesion barrier.

### Appendix G
contains Combination Clusters. This table is used for codes that require more than one ICD-10-PCS procedure code for correct reporting. An example is provided for insertion of a cardiac pacemaker lead into a coronary vein. The additional procedures describe the exact location of where the lead is inserted, which is required for correct reporting. The instructions in the Appendix specify that the first code in the cluster needs to be reported with one or more of the additional codes listed for all codes to be considered valid. 

Appendix H
contains Non-OR Not Affecting MS-DRG Assignment codes.


# Coding Conventions

PCS codes are composed of __seven__ alphanumeric characters. Each character contains up to __34__ possible values. The seven characters that make up a complete code have specific meanings that vary for each of the __17__ sections of the manual.

Each value represents a specific option for the general character definition. 10 digits (`0-9`) and 24 letters (`A-H`, `J-N`, and `P-Z`) may be used in each character. 

> The letters `O` and `I` are not used so as to avoid confusion with the digits `0` and `1`.

## Axes

Each character is an axis of classification that specifies information about the procedure performed. 

Within a defined code range, a character specifies the same type of information in that axis of classification.

For example, The __fifth__ axis of classification specifies the _Approach_ in sections 0 through 4 and 7 through 9 of the system.

```{r echo=FALSE, eval=FALSE}
tables() |> 
  summarise(codes = sum(n_codes),
            prop = codes / 78220, 
            .by = c(section, system)) |>
  left_join(sections()[c('code', 'label')], 
            by = join_by(section == code)) |> 
  left_join(systems()[c('code', 'label')], 
            by = join_by(system == code)) |> 
  select(section = label.x, 
         code = system, 
         system = label.y, 
         codes, 
         prop) |> 
  gt(groupname_col = "section", 
     rowname_col = "system") |>
  fmt_percent(columns = prop, decimals = 2) |>
  fmt_number(columns = codes, decimals = 0) |>
  opt_table_font(font = google_font(name = "Rubik")) |> 
  cols_align(align = "center", columns = code) |>
  cols_label(code = "") |> 
  tab_style(style = list(cell_fill(color = "lightgray", 
                                   alpha = 0.5), 
                         cell_text(weight = "bold")), 
            locations = cells_body(columns = code)) |> 
  opt_all_caps(locations = c("row_group")) |> 
  opt_align_table_header(align = "left") |>
  tab_header(title = html("<b>ICD-10-PCS</b> 2024")) |> 
  tab_options(
    column_labels.hidden = TRUE,
    heading.title.font.size = px(22),
    table.font.size = px(14),
    column_labels.border.bottom.width = px(0),
    column_labels.border.top.width = px(0),
    row_group.font.size = px(16))
```


# Example

```{r}
x <- pcs("0016070")

x$axes |>
  gt(rowname_col = "axis") |>
  opt_table_font(font = google_font(name = "Rubik")) |>
  cols_align(align = "center", columns = c(axis, value)) |>
  tab_style(style = list(cell_fill(color = "lightgray",
                                   alpha = 0.5),
                         cell_text(weight = "bold")),
            locations = cells_body(columns = value)) |>
  opt_all_caps() |>
  tab_header(title = html("<b>ICD-10-PCS 2024</b>"),
             subtitle = html(paste0("<b>", x$code, ": </b>", x$description))) |>
  tab_footnote(
    footnote = html(paste0("<b>Definition:</b> ", 
    fuimus::delister(x$definitions[1, 2]))),
    locations = cells_body(columns = label, rows = 3)) |>
  tab_footnote(
    footnote = html(paste("<b>Includes:</b>", fuimus::delister(x$includes[1, 5]))),
    locations = cells_body(columns = label, rows = 4)) |>
  tab_footnote(
    footnote = html(paste0("<b>Definition:</b> ", 
    fuimus::delister(x$definitions[2, 2]))),
    locations = cells_body(columns = label, rows = 5)) |>
  tab_options(
    table.width = pct(75),
    heading.title.font.size = px(20),
    heading.subtitle.font.size = px(14),
    heading.align = "left",
    table.font.color = "#0B0B45",
    footnotes.font.size = px(12))
```





